The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-27 article.tex
Generate fingerprints of length 7 which is more typical for Daylight-like path based FPs. Results is the same but the times are slightly slower due to the increased cost.
Timing updates in text.

\textbf{-type path}: Path based fingerprints encode paths of length 1...n. n was
choose to be 6 for this benchmark. Path based fingerprints can be used for both
substructure and similarity screening. The algorithm was
tweaked for \cdkversion{} to hash the paths without pre-computing all paths
upfront and without needing to generate character strings before hashing. The 
time to encode ChEMBL previously took 26-35 minutes now only takes $\sim$5 
minutes.

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m14.5s & 32.7K & 9 & 8.67s & 280.9K & 8.59 \\
 &  & sdf & 0 & 1m52.17s & 22.8K & 25 & 12.15s & 210.9K & 9.23 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 35m2.8s & 47.9K & 9 & 5m31.52s & 303.8K & 6.34 \\
 &  & sdf & 0 & 38m51.73s & 43.2K & 0 & 6m19.63s & 265.3K & 6.14 \\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 51.99s & 46.9K & 0 & 7.7s & 316.3K & 6.8 \\
 &  & sdf & 0 & 1m44.96s & 24.4K & 0 & 8.4s & 305K & 12.5 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 26m23.5s & 63.6K & 0 & 5m19.35s & 315.3K & 5 \\
 &  & sdf & 0 & 35m34.44s & 47.2K & 0 & 5m12.4s & 322.4K & 6.8 \\

>>>>

\textbf{-type path}: Path based fingerprints encode paths of length 0 to 7. Path
based fingerprints can be used for both substructure and similarity screening. 
The algorithm was tweaked for \cdkversion{} to hash the paths without 
pre-computing all paths upfront and without needing to generate character 
strings before hashing. The time to encode ChEMBL previously took 42-47 minutes 
now only takes 6-7 minutes.

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m38s & 24.9K & 9 & 10.4s & 234.2K & 9.42 \\
 &  & sdf & 0 & 2m11.03s & 19.6K & 25 & 14.22s & 180.2K & 9.21 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 42m56.15s & 39.1K & 9 & 6m38.67s & 252.6K & 6.46 \\
 &  & sdf & 0 & 47m5.58s & 35.6K & 0 & 7m46.85s & 215.7K & 6.05 \\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 1m15.49s & 32.3K & 0 & 9.43s & 258.3K & 8 \\
 &  & sdf & 0 & 2m3.82s & 20.7K & 0 & 10.47s & 244.7K & 11.8 \\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 34m16.85s & 49K & 0 & 6m26.5s & 260.6K & 5.3 \\
 &  & sdf & 0 & 43m48.29s & 38.3K & 0 & 6m39.62s & 252K & 6.6 \\
